Notes for ISIPTA poster

### 2016-07-27 asce-paper.tex
elicitation section, start examples

\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{url}
\usepackage{tikz}
\usetikzlibrary{shapes.misc,fit}

@@

The paper is organized as follows.
In Section~\ref{sec:weibull}, we describe a Bayesian analysis for Weibull component lifetimes
with fixed shape parameter
and illustrate the issue of prior-data conflict.
Section~\ref{sec:modforsurpr} then details the use of sets of priors
for the scale parameter $\lambda_k$ of the Weibull distribution,
showing how this mitigates the prior-data conflict issue for $\lambda_k$.
Section~\ref{sec:robrel} then exploits this model to calculate system reliability bounds for a running system. 
To this end, Bayesian estimation of $\lambda_k$ under right-censored observations is covered in Section~\ref{sec:lambdawithcens},
followed by a brief introduction to the survival signature (Section~\ref{sec:sysrelwithsurvsign}).
Section~\ref{sec:postpred} then details how gathered information on component lifetimes
is transfomed to the necessary form for use within the survival signature framework,
and Section~\ref{sec:optimize} explains how lower and upper bounds for $\Rsys(t \mid t > \tnow)$
are obtained by efficiently optimizing over the parameter sets that define the sets of priors.
***

@@

We consider a system with components of $k=1,\ldots,K$ different types;
for each type $k$, there are $n_k$ exchangeable components in the system.
For each type $k$ component, we assume for its lifetime $T_i^k$ ($i=1,\ldots,n_k$, $k = 1, \ldots, K$)
a Weibull distribution with fixed shape parameter $\beta_k > 0$,
in short $T_i^k \mid \lambda_k \sim \wei(\beta_k,\lambda_k)$,
with density and cdf%
\begin{linenomath*}
\begin{align}
\label{eq:weibulldens}
f(t_i^k \mid \lambda_k) &= \frac{\beta_k}{\lambda_k} (t_i^k)^{\beta_k-1} e^{-\frac{(t_i^k)^{\beta_k-1}}{\lambda_k}}\,, \\
\label{eq:weibullcdf}
F(t_i^k \mid \lambda_k) &= 1 - e^{-\frac{(t_i^k)^{\beta_k}}{\lambda_k}} = P(T_i^k \leq t_i^k \mid \lambda_k)\,,
\end{align}
\end{linenomath*}
where $\lambda_k > 0$ and $t > 0$.%
\footnote{The shape parameter $\beta_k$ determines whether the hazard rate is increasing ($\beta_k > 1$)
or decreasing ($\beta_k < 1$) over time.
For $\beta_k=1$, we obtain the Exponential distribution with constant hazard rate as a special case.
The value for $\beta_k$ will thus often be clear from practical considerations.}
The scale parameter $\lambda_k$ can be interpreted through the relation
\begin{linenomath*}
\begin{align}
\E[T_i^k \mid \lambda_k] &= \lambda_k^{1/\beta_k}\, \Gamma(1 + 1/\beta_k)\,.
\label{eq:lambdainterpret}
\end{align}
\end{linenomath*}
For encoding expert knowledge about the reliability of the components,
we need to assign a prior distribution over the scale parameter $\lambda_k$.
A convenient choice is to use the inverse Gamma distribution,
commonly parametrized in terms of the hyperparameters $a_k > 0$ and $b_k > 0$:
%Conjugate prior is $\lambda_k \sim \ig(a_k,b_k)$:
\begin{linenomath*}
\begin{align}
f(\lambda_k\mid a_k,b_k) &= \frac{(b_k)^{a_k}}{\Gamma(a_k)} \lambda_k^{-a_k -1} e^{-\frac{b_k}{\lambda_k}}
\label{eq:ig-def}
\end{align}
\end{linenomath*}
in short, $\lambda_k \mid a_k, b_k \sim \ig(a_k,b_k)$.
The inverse Gamma is convenient because it is a conjugate prior,
i.e., the posterior obtained by Bayes' rule is again inverse Gamma and thus easily tractable;
the prior parameters only need to be updated to obtain the posterior parameters.

@@

The structure of complex systems can be visualized by reliability block diagrams,
an example is given in Figure~\ref{fig:bridge-layout}.
Components are represented by boxes or nodes,
and the system works when a path from the left end to the right exists
which passes only through working components.
In a system with $n$ components, the state of the components can be expressed by the state vector
$\vec{x} = (x_1,x_2,\ldots,x_n) \in \{0,1\}^n$, with $x_i=1$ if the $i$th component functions 
and $x_i=0$ if not.
The structure function $\phi : \{0,1\}^n \rightarrow \{0,1\}$, defined for all possible $\vec{x}$, takes 
the value 1 if the system functions and 0 if the system does not function for state vector $\vec{x}$
\cite{BP75}.
Most real-life systems are coherent,
which means that $\phi(\vec{x})$ is non-decreasing in any of the components of $\vec{x}$,
so system functioning cannot be improved by worse performance of one or more of its components.
Furthermore, one can usually assume that $\phi(0, \ldots, 0) = 0$ and $\phi(1, \ldots, 1) = 1$.

@@

Writing out \eqref{eq:sysrel-survsign}, we get
\begin{linenomath*}
\begin{align}
\lRsys(t \mid t > \tnow)
 &= \min_{\PZi{1},\ldots,\PZi{K}} \Rsys\big(t \mid t > \tnow, \cup_{k=1}^K \{\PkZ, \vec{t}^k_{e_k;n_k}\}\big) \nonumber\\
 &= \min_{\substack{\nkzfun{1} \in \left[\nkzlfun{1}, \nkzufun{1}\right]\\ \vdots\\ \nkzfun{K} \in \left[\nkzlfun{K}, \nkzufun{K}\right]}}
    \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K P(C^k_t = l_k\mid\nkz,\ykzl, \mbf{t}^k_{e_k;n_k})\,,
\end{align}
\end{linenomath*}
such that a $K$-dimensional box-constraint optimization is needed to obtain $\lRsys(t \mid t > \tnow)$.
The result for $\uRsys(t \mid t > \tnow)$ is completely analogous.
Computing time can furthermore be saved
by computing only those $P(C^k_t = l_k\mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ for $l_k$'s for which $\Phi(l_1,\ldots,l_K) > 0$.

@@

\section{Elicitation of prior parameter sets}

*** prior via pseudo-observations, can contain censored pseudo-data

*** cf paper from Frank \cite{1996:coolen::cens}

\section{Examples}

***from poster, bridge type system Fig.~\ref{fig:bridge-layout}, or brake system from ijar paper?

we use box-constraint optimization with option \texttt{L-BFGS-B} of \texttt{optim} in \textsf{R}.

\begin{figure}
\centering
\begin{tikzpicture}
[type1/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
 type2/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
 type3/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
 cross/.style={cross out,draw=red,very thick,minimum width=7mm, minimum height=5mm},
 hv path/.style={thick, to path={-| (\tikztotarget)}},
 vh path/.style={thick, to path={|- (\tikztotarget)}}]
%\begin{scope}[scale=0.75]
\node[type1] (T3)   at ( 5.6, 0) {T3};
\node[type2] (T2)   at ( 2.8, 0) {T2};
\node[type3] (T1-2) at ( 1.4, 1) {T1};
\node[type3] (T1-3) at ( 1.4,-1) {T1};
\node[type3] (T1-5) at ( 4.2, 1) {T1};
\node[type3] (T1-6) at ( 4.2,-1) {T1};
\coordinate (start) at (0  ,0);
\coordinate (end)   at (6.3,0);
\coordinate (bista) at (0.7,0);
\coordinate (biend) at (4.9,0);
\path (bista)     edge[hv path] (start)
                  edge[vh path] (T1-2.west)
                  edge[vh path] (T1-3.west)
      (T1-2.east) edge[hv path] (T2.north)
      (T1-3.east) edge[hv path] (T2.south)
      (T2.north)  edge[vh path] (T1-5.west)
      (T2.south)  edge[vh path] (T1-6.west)
      (biend)     edge[vh path] (T1-5.east)
                  edge[vh path] (T1-6.east)
                  edge[hv path] (T3.west)
      (T3.east)   edge[hv path] (end);
%\end{scope}
\end{tikzpicture}
\caption{Reliability block diagram for a `bridge' system with three component types.}
\label{fig:bridge-layout}
\end{figure}

\section{Concluding Remarks}

>>>>

\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{booktabs}
\usepackage{url}
\usepackage{tikz}
%\usetikzlibrary{shapes.misc,fit}
\usetikzlibrary{%
   arrows,%
   calc,%
   fit,%
   patterns,%
   plotmarks,%
   shapes.geometric,%
   shapes.misc,%
   shapes.symbols,%
   shapes.arrows,%
   shapes.callouts,%
   shapes.multipart,%
   shapes.gates.logic.US,%
   shapes.gates.logic.IEC,%
   er,%
   automata,%
   backgrounds,%
   chains,%
   topaths,%
   trees,%
   petri,%
   mindmap,%
   matrix,%
   calendar,%
   folding,%
   fadings,%
   through,%
   patterns,%
   positioning,%
   scopes,%
   decorations.fractals,%
   decorations.shapes,%
   decorations.text,%
   decorations.pathmorphing,%
   decorations.pathreplacing,%
   decorations.footprints,%
   decorations.markings,%
   shadows}

@@

The paper is organized as follows.
In Section~\ref{sec:weibull}, we describe a Bayesian analysis for Weibull component lifetimes
with fixed shape parameter
and illustrate the issue of prior-data conflict.
Section~\ref{sec:modforsurpr} then details the use of sets of priors
for the scale parameter $\lambda_k$ of the Weibull distribution,
showing how this mitigates the prior-data conflict issue for $\lambda_k$.
Section~\ref{sec:robrel} then develops a method to calculate system reliability bounds
for a running system based on sets of priors for $\lambda_k$. 
%To this end, Bayesian estimation of $\lambda_k$ under right-censored observations is covered in Section~\ref{sec:lambdawithcens},
%followed by a brief introduction to the survival signature (Section~\ref{sec:sysrelwithsurvsign}).
%Section~\ref{sec:postpred} then details how gathered information on component lifetimes
%is transfomed to the necessary form for use within the survival signature framework,
%and Section~\ref{sec:optimize} explains how lower and upper bounds for $\Rsys(t \mid t > \tnow)$
%are obtained by efficiently optimizing over the parameter sets that define the sets of priors.
Section~\ref{sec:elicitation} discusses elicitation,
by giving guidelines on how to choose prior parameter bounds
that reflect expert information on components;
Section~\ref{sec:examples} contains examples illustrating ***.
Section~\ref{sec:concluding} concludes the paper by *** 
***

@@

We consider a system with components of $k=1,\ldots,K$ different types;
for each type $k$, there are $n_k$ exchangeable components in the system.
For each type $k$ component, we assume for its lifetime $T_i^k$ ($i=1,\ldots,n_k$, $k = 1, \ldots, K$)
a Weibull distribution with fixed shape parameter $\beta_k > 0$,
in short $T_i^k \mid \lambda_k \sim \wei(\beta_k,\lambda_k)$,
with density and cdf%
\begin{linenomath*}
\begin{align}
\label{eq:weibulldens}
f(t_i^k \mid \lambda_k) &= \frac{\beta_k}{\lambda_k} (t_i^k)^{\beta_k-1} e^{-\frac{(t_i^k)^{\beta_k}}{\lambda_k}}\,, \\
\label{eq:weibullcdf}
F(t_i^k \mid \lambda_k) &= 1 - e^{-\frac{(t_i^k)^{\beta_k}}{\lambda_k}} = P(T_i^k \leq t_i^k \mid \lambda_k)\,,
\end{align}
\end{linenomath*}
where $\lambda_k > 0$ and $t > 0$.%
\footnote{The shape parameter $\beta_k$ determines whether the hazard rate is increasing ($\beta_k > 1$)
or decreasing ($\beta_k < 1$) over time.
For $\beta_k=1$, we obtain the Exponential distribution with constant hazard rate as a special case.
The value for $\beta_k$ will thus often be clear from practical considerations.}
The scale parameter $\lambda_k$ can be interpreted through the relation
\begin{linenomath*}
\begin{align}
\E[T_i^k \mid \lambda_k] &= \lambda_k^{1/\beta_k}\, \Gamma(1 + 1/\beta_k)\,.
\label{eq:lambdainterpret}
\end{align}
\end{linenomath*}
For encoding expert knowledge about the reliability of the components,
we need to assign a prior distribution over the scale parameter $\lambda_k$.
A convenient choice is to use the inverse Gamma distribution,
commonly parametrized in terms of the hyperparameters $a_k > 0$ and $b_k > 0$:
%Conjugate prior is $\lambda_k \sim \ig(a_k,b_k)$:
\begin{linenomath*}
\begin{align}
f(\lambda_k\mid a_k,b_k) &= \frac{(b_k)^{a_k}}{\Gamma(a_k)} \lambda_k^{-a_k -1} e^{-\frac{b_k}{\lambda_k}}
\label{eq:ig-def}
\end{align}
\end{linenomath*}
in short, $\lambda_k \mid a_k, b_k \sim \ig(a_k,b_k)$.
The inverse Gamma is convenient because it is a conjugate prior,
i.e., the posterior obtained by Bayes' rule is again inverse Gamma and thus easily tractable;
the prior parameters only need to be updated to obtain the posterior parameters.

@@

The structure of complex systems can be visualized by reliability block diagrams,
an example is given in Figure~\ref{fig:brakesys-layout}.
Components are represented by boxes or nodes,
and the system works when a path from the left end to the right exists
which passes only through working components.
In a system with $n$ components, the state of the components can be expressed by the state vector
$\vec{x} = (x_1,x_2,\ldots,x_n) \in \{0,1\}^n$, with $x_i=1$ if the $i$th component functions 
and $x_i=0$ if not.
The structure function $\phi : \{0,1\}^n \rightarrow \{0,1\}$, defined for all possible $\vec{x}$, takes 
the value 1 if the system functions and 0 if the system does not function for state vector $\vec{x}$
\cite{BP75}.
Most real-life systems are coherent,
which means that $\phi(\vec{x})$ is non-decreasing in any of the components of $\vec{x}$,
so system functioning cannot be improved by worse performance of one or more of its components.
Furthermore, one can usually assume that $\phi(0, \ldots, 0) = 0$ and $\phi(1, \ldots, 1) = 1$.

@@

Writing out \eqref{eq:sysrel-survsign}, we get
\begin{linenomath*}
\begin{align}
\lRsys(t \mid t > \tnow)
 &= \min_{\PZi{1},\ldots,\PZi{K}} \Rsys\big(t \mid t > \tnow, \cup_{k=1}^K \{\PkZ, \vec{t}^k_{e_k;n_k}\}\big) \nonumber\\
 &= \min_{\substack{\nkzfun{1} \in \left[\nkzlfun{1}, \nkzufun{1}\right]\\ \vdots\\ \nkzfun{K} \in \left[\nkzlfun{K}, \nkzufun{K}\right]}}
    \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K P(C^k_t = l_k\mid\nkz,\ykzl, \mbf{t}^k_{e_k;n_k})\,,
\end{align}
\end{linenomath*}
such that a $K$-dimensional box-constraint optimization is needed to obtain $\lRsys(t \mid t > \tnow)$.
The result for $\uRsys(t \mid t > \tnow)$ is completely analogous.
Computing time can furthermore be saved
by computing only those %$P(C^k_t = l_k\mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ for $l_k$'s for which $\Phi(l_1,\ldots,l_K) > 0$
summation terms for which $\Phi(l_1,\ldots,l_K) > 0$.

@@

\section{Elicitation of prior parameter sets}
\label{sec:elicitation}

To represent expert knowledge on component failure times
through bounds for $\ykz$ and $\nkz$,
we can refer to the interpretations as given in Section~\ref{sec:weibull}:
$\ykz$ is the prior expected value of $\lambda_k$,
where $\lambda_k$ is linked to expected component lifetimes through \eqref{eq:lambdainterpret}.
$\nkz$ can be seen as pseudocount, indicating how strong expert knwoledge is trusted
in comparison to a sample of size $n$.
Our approach allows the expert to give ranges $[\ykzl, \ykzu]$ and $[\nkzl, \nkzu]$
instead of forcing a precise answer.

It is also possible to directly link $\nkz$ and $\ykz$
to observed lifetimes using a prior predictive distribution.
Dropping the component index $k$ for ease of notation, this is given by
\begin{linenomath*}
\begin{align}
f(t\mid \nz, \yz)
 &= \int f(t\mid \lambda) f(\lambda\mid\nz,\yz) \dd \lambda \nonumber\\
 &= \beta\, t^{\beta - 1}\, (\nz + 1) \frac{(\nz \yz)^{\nz + 1}}{(\nz \yz + t^\beta)^{\nz + 2}} \,.
\label{eq:tpriopred}
\end{align}
\end{linenomath*}
Replacing the prior parameters $\nz$ and $\yz$
with their posterior counterparts $\nn$ and $\yn$ as defined in \eqref{eq:ig-update},
the effect of virtual observations on \eqref{eq:tpriopred}, or the corresponding reliability function, can be determined.
This allows to determine $\nz$ and $\yz$ through a number of `what-if' scenarios,
by asking the expert to state what (s)he would expect to learn from observing certain virtual data.

This strategy is known as pre-posterior analysis,
being first advocated by \citeN[p.~19]{1965:good}.
We recommend to check whether the effects of $\PkZ$ on the inference of interest
(this may not always be the full reliability function)
reasonably reflect an expert's beliefs before the data and in case some specific data become available,
both data agreeing with initial beliefs and surprising data.
Essentially, we advise to do an analysis like in our examples in Section~\ref{sec:examples} below,
using hypothetical data.

To elicit a meaningful prior distribution, or a set of prior distributions,
it is important to ask questions which enable experts to stay close to their actual expertise.
\citeN{1996:coolen::cens} discussed the possibility of generalizing the usual conjugate prior distributions,
for parameters of exponential family models, by including pseudo-data which are right-censored.
If the real data set contains such values, then such generalized priors do not lead to more computational complexities,
while they can have several advantages.
In addition to providing slightly more general classes of prior distributions through an additional hyperparameter,
they may enable more realistic elicitation of expert judgements,
for example if the expert has no experience with certain components past a specific life time.
For more details we refer to \citeN{1996:coolen::cens},
it should be noted that adopting such generalized prior distributions
may also provide more flexibility for modelling the effects of prior-data conflict,
this is left as a topic for future research.

\begin{figure}
\centering
\begin{tikzpicture}
[typeM/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=8mm}, %font=\footnotesize},
 typeC/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=8mm}, %font=\footnotesize},
 typeP/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=8mm}, %font=\footnotesize},
 typeH/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=8mm}, %font=\footnotesize},
 type1/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
 type2/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
 type3/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
 cross/.style={cross out,draw=red,very thick,minimum width=7mm, minimum height=5mm},
 hv path/.style={thick, to path={-| (\tikztotarget)}},
 vh path/.style={thick, to path={|- (\tikztotarget)}}]
\begin{scope}[scale=1.5]
\node[typeM] (M)    at ( 0  , 0  ) {M};
\node[typeC] (C1)   at ( 1  , 1.5) {C1};
\node[typeC] (C2)   at ( 1  , 0.5) {C2};
\node[typeC] (C3)   at ( 1  ,-0.5) {C3};
\node[typeC] (C4)   at ( 1  ,-1.5) {C4};
\node[typeP] (P1)   at ( 2  , 1.5) {P1};
\node[typeP] (P2)   at ( 2  , 0.5) {P2};
\node[typeP] (P3)   at ( 2  ,-0.5) {P3};
\node[typeP] (P4)   at ( 2  ,-1.5) {P4};
\node[typeH] (H)    at ( 0  ,-1  ) {H};
\coordinate (start)  at (-0.7, 0);
\coordinate (startC) at ( 0.5, 0);
\coordinate (startH) at (-0.4, 0);
\coordinate (Hhop1)  at ( 0.4,-1);
\coordinate (Hhop2)  at ( 0.6,-1);
\coordinate (endP)   at ( 2.5, 0);
\coordinate (end)    at ( 2.8, 0);
\path (start)     edge[hv path] (M.west)
      (M.east)    edge[hv path] (startC)
      (startC)    edge[vh path] (C1.west)
                  edge[vh path] (C2.west)
                  edge[vh path] (C3.west)
                  edge[vh path] (C4.west)
      (C1.east)   edge[hv path] (P1.west)
      (C2.east)   edge[hv path] (P2.west)
      (C3.east)   edge[hv path] (P3.west)
      (C4.east)   edge[hv path] (P4.west)
      (endP)      edge[vh path] (P1.east)
                  edge[vh path] (P2.east)
                  edge[vh path] (P3.east)
                  edge[vh path] (P4.east)
                  edge[hv path] (end)
      (startH)    edge[vh path] (H.west)
      (H.east)    edge[hv path] (Hhop1)
      (Hhop1)     edge[thick,out=90,in=90] (Hhop2)
      (Hhop2)     edge[hv path] (P3.south)
                  edge[hv path] (P4.north);
\end{scope}
\end{tikzpicture}
\caption{Reliability block diagram for a simplified automotive brake system.}
\label{fig:brakesys-layout}
\end{figure}

\section{Examples}
\label{sec:examples}

%***brake system from ijar paper, Fig.~\ref{fig:brakesys-layout}
As illustrative example, we consider a simplified automotive brake system with four types of component.
The system layout is depicted in Figure~\ref{fig:brakesys-layout}.
The master brake cylinder (M) activates all four wheel brake cylinders (C1 -- C4),
which in turn actuate a braking pad assembly each (P1 -- P4).
The hand brake mechanism (H) goes directly to the brake pad assemblies P3 and P4;
the car brakes when at least one brake pad assembly is actuated.
All values for $\Phi \not\in \{0,1\}$ for this system are given in Table~\ref{tab:brake-survsign}.

\begin{table}
\centering
\begin{tabular}{cccclcccccl}
  \toprule
M & H & C & P & $\Phi$ & \quad & M & H & C & P & $\Phi$\\ 
  \midrule
1 & 0 & 1 & 1 & 0.25 & & 1 & 0 & 2 & 1 & 0.50 \\ 
1 & 0 & 1 & 2 & 0.50 & & 1 & 0 & 2 & 2 & 0.83 \\ 
1 & 0 & 1 & 3 & 0.75 & & 1 & 0 & 3 & 1 & 0.75 \\ 
0 & 1 & 0 & 1 & 0.50 & & 1 & 1 & 0 & 1 & 0.50 \\ 
0 & 1 & 0 & 2 & 0.83 & & 1 & 1 & 0 & 2 & 0.83 \\ 
0 & 1 & 1 & 1 & 0.62 & & 1 & 1 & 1 & 1 & 0.62 \\ 
0 & 1 & 1 & 2 & 0.92 & & 1 & 1 & 1 & 2 & 0.92 \\ 
0 & 1 & 2 & 1 & 0.75 & & 1 & 1 & 2 & 1 & 0.75 \\ 
0 & 1 & 2 & 2 & 0.97 & & 1 & 1 & 2 & 2 & 0.97 \\ 
0 & 1 & 3 & 1 & 0.88 & & 1 & 1 & 3 & 1 & 0.88 \\ 
   \bottomrule
\end{tabular}
\caption{Survival signature values $\not\in \{0,1\}$ for the simplified automotive brake system depicted in Figure~\ref{fig:brakesys-layout}.}
\label{tab:brake-survsign}
\end{table}

***we use box-constraint optimization via option \texttt{L-BFGS-B} of \texttt{optim} in \textsf{R}.

\section{Concluding Remarks}
\label{sec:concluding}
